Factoring with $n+2$ clean qubits and $n-1$ dirty qubits

### 2017-05-17 doc/paper.tex
Use new test methods in multi_not_test

We presented Toffoli-based arithmetic circuits that reduce the smallest known number of qubits required to perform Shor's algorithm from $2n+2$ to $2n+1$.
The constructions also reduce the number of {\em clean} qubits required by $n$, so the number of clean qubits required is now $n + O(1)$.
We consider this to be a step towards a period-finding construction that uses only $n + O(1)$ qubits total, which could reduce the expected lifetime of current cryptographic keys by months or years (depending on how quickly quantum computers gain error-corrected capacity).

>>>>

We presented Toffoli-based arithmetic circuits that reduce the smallest known number of qubits required to perform Shor's algorithm from $2n+2$ to $2n+1$.
The constructions also reduce the number of {\em clean} qubits required by $n$, so the number of clean qubits required is now $n + O(1)$.
We consider this to be a step towards a period-finding construction that uses only $n + O(1)$ qubits total, which could reduce the expected lifetime of current cryptographic keys by years (depending on how quickly quantum computers gain error-corrected capacity).
